---
title: "Weight of Fish"
author: "Eileen Dunn"   
date: "July 30th, 2024"   
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}

if(!require("Bolstad")) {install.packages("Bolstad");require("Bolstad")}
```

## Perch

```{r}
perchmodel=lm(Weight~ .,data=Perch)
summary.lm(perchmodel)
```  

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best two regressor model is H-W.  

### Best Two regressor model

```{r}
Perch2model=lm(Weight~Height+Width,data = Perch)
summary.lm(Perch2model)
```

The best two regressor model used to determine weight for Perch is using height and weight(H-W)  

## Pike

```{r}
Pikemodel1=lm(Weight~ .,data=Pike)
summary.lm(Pikemodel1)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The regressor shows that L1-L-3-W is greater.  

### Best Two regressor model

```{r}
Pike2Model=lm(Weight~Length1+Length3,data = Pike)
summary.lm(Pike2Model)
```

The best regressor model for predicting weight for Pike is using Length 1 and Length 3.  


## Roach

### Best Models

```{r}
Roach1Model=lm(Weight~ ., data=Roach)
summary.lm(Roach1Model)
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The regressor shows that L3-W is greater.  

### Best Two regressor model


```{r}
Roach2Model=lm(Weight~Length3-Width,data = Roach)
summary.lm(Roach2Model)
```

The Best regressor model for predicting weight for Roach is using Length 3 and Width.  


## Final Summary Statements

The results above for Perch say that the best two regressor model used to predict weight for Perch is using height and weight(H-W). The results also showed that the best regressor model for predicting weight for Pike is using Length 1 and Length 3. The results for Roach showed that the best regressor model for predicting weight for Roach is using Length 3 and Width.  


